---
title: "Exercise 02"
output: pdf_document
---

```{r setup, include=FALSE, chache = F}
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = TRUE)
```

\let\OldRule\rule
\renewcommand{\rule}[2]{\OldRule{\linewidth}{#2}}

----------

# Task 2

# Task 2.1
```{r}
label <- factor(c("HR", "KS", "KS", "GOE", "KS", "ESW", "HR", "KS", "KS", "KS"))
persons <- c(4, 2, 1, 5, 1, 2, 3, 1, 2, 1)
speed <- c(75.5, 68.2, 65.3, 60.1, 80.9, 100.0, 87.0, 70.2, 72.5, 69.6)

df <- data.frame(label, persons, speed)
df
```

# Task 2.1.a
```{r}
barplot(table(df$label),
        main = "Absolute frequency of car labels",
        xlab = "Car label", ylab = "Absolute frequency")
barplot(table(df$label) / length(df$label),
        main = "Relative frequency of car labels",
        xlab = "Car label", ylab = "Relative frequency")
barplot(table(df$persons),
        main = "Absolute frequency of persons",
        xlab = "Number of persons", ylab = "Absolute frequency")
barplot(table(df$persons) / length(df$persons),
        main = "Relative frequency of persons",
        xlab = "Number of persons", ylab = "Relative frequency")
hist(df$speed,
     main = "Absolute frequency of speed",
     xlab = "Speed", ylab = "Absolute frequency", breaks = 10)
hist(df$speed / length(df$speed),
     main = "Relative frequency of speed",
     xlab = "Speed", ylab = "Relative frequency", breaks = 10)
```

# Task 2.1.b
```{r}
# TODO: Import image from file with handdrawn diagram
```

# Task 2.1.c
```{r}
plot(ecdf(df$persons),
     main = "Empirical cumulative distribution function of persons",
     xlab = "Number of persons", ylab = "ECDF")
```

# Task 2.1.d
The data in the dataframe were already created as frequency tables in task 2.1.a, which is why they are deliberately omitted here.
Likewise, it makes little sense to generate additional bar plots here because the absolute and relative frequency plots are already bar plots.
For this reason, only the staff diagram, histogram, and distribution function are shown below.
```{r}
plot(table(df$label), type = "h",
     main = "Staff diagram of car labels",
     xlab = "Car label", ylab = "Absolute frequency")
plot(table(df$persons), type = "h",
     main = "Staff diagram of persons",
     xlab = "Number of persons", ylab = "Absolute frequency")
plot(table(df$speed), type = "h",
     main = "Staff diagram of speed",
     xlab = "Speed", ylab = "Absolute frequency")
hist(df$persons,
     main = "Histogram of persons",
     xlab = "Number of persons", ylab = "Absolute frequency")
hist(df$speed,
     main = "Histogram of speed",
     xlab = "Speed", ylab = "Absolute frequency")
# TODO: distribution function
```