---
title: "Homework 02"
output: pdf_document
---

```{r setup, include=FALSE, chache = F}
knitr::opts_knit$set(root.dir = normalizePath(".."))
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(error = TRUE)
```

\let\OldRule\rule
\renewcommand{\rule}[2]{\OldRule{\linewidth}{#2}}

----------

# Task 2
## Task 2.7
```{r}
auto <- read.table("data/auto.txt", header = TRUE)
names(auto) <- c("No", "Origin", "Price", "Consumption",
                 "Interior damage", "Body damage", "Tank")
auto$Origin <- factor(auto$Origin,
                      levels = c(1, 2, 3, 4),
                      labels = c("GER", "AUT", "CH", "FR"))
```

### Task 2.7.a
Characteristic $X_1$ should be displayed as a bar chart, since these are nominal values.
```{r}
barplot(table(auto$Origin),
        main = "Bar chart - Country of origin of the cars",
        xlab = "Origin",
        ylab = "Absolute frequency")
```

The estimated value in euros should be categorized into different price classes, otherwise all frequencies would be 1 in a bar or column chart. Since a class width is used, a histogram is suitable for graphical representation.
```{r}
hist(auto$Price,
     main = "Histogram - Price of the cars",
     xlab = "Price in euros",
     ylab = "Absolute frequency",
     breaks = 2)
```